%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Piyush Singhai}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

       				                      \hfill phone: 09930493127, 08319619710      \vspace{0mm}\\\vspace{0mm}%
        					      \hfill e-mail: singhai.piyush@gmail.com  \vspace{0mm}\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{IIT Guwahati, Assam} \hfill \textbf{2007 -- 2009}\vspace{0mm}\\\vspace{0mm}%
    \textsl{M.Tech in Computer Science} \hfill \textsl{CGPA: 9.16/10}

    \textbf{IES IPS Academy Indore, MP} \hfill \textbf{2003 -- 2007}\vspace{0mm}\\\vspace{0mm}%
    \textsl{B.E. in Computer Science} \hfill \textsl{Percentage: 78\%}

    \textbf{Saraswati Shishu Mandir Indore} \hfill \textbf{June 2003}\vspace{0mm}\\\vspace{0mm}%
    \textsl{MP Board- XIIth} \hfill \textsl{Percentage: 72.8\%}

  %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Relevant Tools}
     \begin{itemize}
      \item OS : Linux, Windows
      \item Programming Languages: Python, C/C++, Java
      \item Frameworks/Applications: Docker, Redis, Django, DCOS, \\
            Apache, FreeSWITCH, Mysql, Aurora RDS, MSSQL, RabbitMQ
      \item OpsViz: Grafana, Telegraf, StatsD, Logstash, InfluxDB
     \end{itemize}

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Work Experience}
    
     \textbf{Oracle, Bangalore }\hfill \textsl{Mar 2018 -- Present}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Principal Member of Techinial Staff}  
    \begin{itemize}
    \item \textsl{OCI Cloud: Exadata Cloud Service Platform }: 
    \begin{enumerate}
    \item Build a Platform for Exadata Cloud Infrastructure 
    \item Created multiple MicroServices for Fleet Manager,  VM Manager.
    \item Build a Rolling Upgrade Solution for Zero downtime upgrade for HA System
    \item Rest API Development for Horizontal scaling of cpu, memory, storage.
    \end{enumerate}
    \end{itemize}

    \textbf{ScaleArc, Mumbai, Maharashtra }\hfill \textsl{Dec 2013 -- Jan 2018}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Senior Member of Techinial Staff-II}      \begin{itemize}
    \item \textsl{DBaaS: DataBase as a Service Platform}: 
    \begin{enumerate}
    \item Build a Platform using DCOS and Marathon
    \item Created multiple MicroServices for Health Monitoring, Failover, User Management etc.
    \item Run Scalearc Proxy inside the Container
    \item Use OpsViz stack to Show Live monitor Graph and Real time Counters
    \end{enumerate}
    
    \item Python API and Services
    \begin{enumerate}
    \item Research on Multiple Replication Technology of Mysql, MSSQL, Oracle and build a Automatic Failover Solution.  
    \item Created a Services like Always On, Replication Monitor, Cluster Monitor etc.
    \item Build Django Based API for Services and UI to communicate each other.
    \item Design and Developed the Scalearc Installer using Puppet, Yum and RPM.
    \item Worked on different issues related to Scalabilty of Services and Inter process communication of services.
    \end{enumerate}
    \end{itemize}
      
    \textbf{Mettl, Gurgaon, Haryana }\hfill \textsl{June 2013 -- Dec 2013}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Senior Software Engineer}   
    \begin{itemize}
    \item Worked For online Maths Platform Tutrr which enables students to practice maths
    \item Worked on Advance Python Features, Maths complex lib Sympy
    \end{itemize}
    
    \textbf{Knowlarity Communication, Gurgaon, Haryana}   \hfill \textsl{June 2010 -- July 2013} \vspace{0mm}\\\vspace{0mm}%
           \textsl{Senior Software Engineer} 
    \begin{itemize}
     \item \textsl{Knowlus: Design and Development of Telephony Platform:} \\
       A Telephony Platform that consists of Multiple Services like Incalld, Outcalld and FreeSWITCH to build solutions for virtual call centers, call bridging, conferences, fax and voicemail.
      
     \item \textsl{Android Application Development:} \\
      Development of several android application for various products like ERCC, RSBY(Goverment Project), SUPERFAX.
     \item Designed and implemented several application based on the above infrastructure:
        \begin{enumerate}
         \item Design and Develop the Product SuperFax.
         \item Worked for different module of SuperReceptionist.
	     \item Watermarking, OCR, Bar code detection for fax files.
	     \item Worked on Scalability issues like Bulk Call, IVR Cache, Call Packet missing, call hangup etc.
        \end{enumerate}
    \end{itemize}

    \textbf{John Deere, Pune, Maharashtra }\hfill \textsl{July 2009 -- June 2010}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Post Graduate Engineering Trainees} 
     \begin{itemize}
     \item \textsl{Distributed Computing and Machine Diagnostics:} 
            \begin{itemize}
             \item To configure Hadoop distributed file system (HDFS) and Hadoop Database (HBase)
             \item The development has been done in a Hadoop platform. Responsibilities include configure hadoop and run Map Reduce Programs.
             \end{itemize}
     \item \textsl{Machine Learning using Artificial Intelligence:}
             \begin{itemize}
              \item This project requires understanding of Artificial Intelligence, Neural Network and development in Encog (Java Based Framework for Neural Network).
	       \item A Research project to analyze diagnosis errors thrown by CAN (Control Area  Network) Bus,
   connected to a tractor, by using several network learning algorithms like Feed Forward Neural Network using Backward Propagation and Redial Basis Functional Neural Network.
               \end{itemize}
      \end{itemize}
    %__________________________________________________________________________________________________________________
    % Other Projects
    \section{\mysidestyle Mtech Thesis and Other Projects}

    \textbf{Proxy Signature Scheme and its application}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Network Security and Cryptography}  \hfill \textsl{July 2007 -- June 2009}
       \begin{itemize}
	\item Proxy Signature allow the original signer to delegate his signing power to a person 
         called proxy signer  who can replace the original signer, in case of temporal absence ,lack of time or computation power etc.
        We evaluate the existing scheme and proposed an efficient and secure proxy signature scheme based on Elliptic Curve 
        Cryptography. 
	\item Guide: Dr. Sukumar Nandi (Prof. of CSE Dept., IIT Guwahati)
       \end{itemize}
       
    \textbf{Tata International Limited (TIL), Dewas, MP} \hfill \textsl{Dec 2006 -- July 2007}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Department: IT} \hfill \textsl{Intern-IT}
     \begin{itemize}
     \item \textsl{Product Enquiry System through Web Mail:} 
            \begin{itemize}
             \item Designed a system for reading and answering the mail from INBOX of company that have a provision for automatic searching and replies of the unanswered queries.
	      \end{itemize}
     \end{itemize}

    %__________________________________________________________________________________________________________________
    % Other Projects
    %__________________________________________________________________________________________________________________
    % Certifications
    \section{\mysidestyle Certifications and Paper Publish}
     \begin{itemize}
      \item Sun Certified Programmer (SCJP) for Java 2 Platform 1.5
      \item Published the Paper on Digital Signature Based Proxy Signature Scheme where proposed ECDLP based solution for this scheme.
\end{itemize}

     
 \section{\mysidestyle Academic Achievements}
\begin{itemize}
  \item Stood among top 2\% in GATE 2007 in CSE.
   \item Secured 2nd rank on the basis of overall performance in B.E in CSE branch
\item Qualified in TON (Programming contest) in Techniche held at IIT-Guwahati. 
\item Qualified in Google Code Jam (Programming contest), an annual coding event conducted by Google Inc.
\item Worked as Teaching Assistant for Data Structures/OOPS/C courses.
\item Attended the Information Security Education and Awareness (ISEA) Project held in IIT Guwahati.
 \end{itemize}

                                                                                                                                          




%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

